Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-06-27 paper/aps_instructions.tex
Add paper sections

\author{Kosala Herath}
 % \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
\author{Malin Premaratne}%
 \email{Second.Author@institution.edu}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%

\collaboration{MUSO Collaboration}%\noaffiliation

\author{Charlie Author}
 \homepage{http://www.Second.institution.edu/~Charlie.Author}
\affiliation{
 Second institution and/or address\\
 This line break forced% with \\
}%
\affiliation{
 Third institution, the second for Charlie Author
}%
\author{Delta Author}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%

\collaboration{CLEO Collaboration}%\noaffiliation

@@

\begin{abstract}
An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article.
\begin{description}
\item[Usage]
Secondary publications and information retrieval purposes.
\item[Structure]
You may use the \texttt{description} environment to structure your abstract;
use the optional argument of the \verb+\item+ command to give the category of each item.
\end{description}
\end{abstract}

@@

\section{\label{sec:level1}First-level heading:\protect\\ The line
break was forced \lowercase{via} \textbackslash\textbackslash}

@@

The \verb+\label{#1}+ should appear
within the section heading,
within the footnote text,
within the equation, or
within the table or figure caption.
The \verb+\ref{#1}+ command
is used in text at the point where the reference is to be displayed.
Some examples: Section~\ref{sec:level1} on page~\pageref{sec:level1},
Table~\ref{tab:table1},%
\begin{table}[b]%The best place to locate the table environment is directly after its first reference in text
\caption{\label{tab:table1}%
A table that fits into a single column of a two-column layout.
Note that REV\TeX~4 adjusts the intercolumn spacing so that the table fills the
entire width of the column. Table captions are numbered
automatically.
This table illustrates left-, center-, decimal- and right-aligned columns,
along with the use of the \texttt{ruledtabular} environment which sets the
Scotch (double) rules above and below the alignment, per APS style.
}
\begin{ruledtabular}
\begin{tabular}{lcdr}
\textrm{Left\footnote{Note a.}}&
\textrm{Centered\footnote{Note b.}}&
\multicolumn{1}{c}{\textrm{Decimal}}&
\textrm{Right}\\
\colrule
1 & 2 & 3.001 & 4\\
10 & 20 & 30 & 40\\
100 & 200 & 300.0 & 400\\
\end{tabular}
\end{ruledtabular}
\end{table}
and Fig.~\ref{fig:epsart}.%
\begin{figure}[b]
\includegraphics{fig_1}% Here is how to import EPS art
\caption{\label{fig:epsart} A figure caption. The figure captions are
automatically numbered.}
\end{figure}

@@

Use the \texttt{figure} environment for a figure, the \texttt{table} environment for a table.
In each case, use the \verb+\caption+ command within to give the text of the
figure or table caption along with the \verb+\label+ command to provide
a key for referring to this figure or table.
The typical content of a figure is an image of some kind;
that of a table is an alignment.%
\begin{figure*}
\includegraphics{fig_2}% Here is how to import EPS art
\caption{\label{fig:wide}Use the figure* environment to get a wide
figure that spans the page in \texttt{twocolumn} formatting.}
\end{figure*}
\begin{table*}
\caption{\label{tab:table3}This is a wide table that spans the full page
width in a two-column layout. It is formatted using the
\texttt{table*} environment. It also demonstates the use of
\textbackslash\texttt{multicolumn} in rows with entries that span
more than one column.}
\begin{ruledtabular}
\begin{tabular}{ccccc}
 &\multicolumn{2}{c}{$D_{4h}^1$}&\multicolumn{2}{c}{$D_{4h}^5$}\\
 Ion&1st alternative&2nd alternative&lst alternative
&2nd alternative\\ \hline
 K&$(2e)+(2f)$&$(4i)$ &$(2c)+(2d)$&$(4f)$ \\
 Mn&$(2g)$\footnote{The $z$ parameter of these positions is $z\sim\frac{1}{4}$.}
 &$(a)+(b)+(c)+(d)$&$(4e)$&$(2a)+(2b)$\\
 Cl&$(a)+(b)+(c)+(d)$&$(2g)$\footnotemark[1]
 &$(4e)^{\text{a}}$\\
 He&$(8r)^{\text{a}}$&$(4j)^{\text{a}}$&$(4g)^{\text{a}}$\\
 Ag& &$(4k)^{\text{a}}$& &$(4h)^{\text{a}}$\\
\end{tabular}
\end{ruledtabular}
\end{table*}

@@

Video~\ref{vid:PRSTPER.4.010101}
illustrates several features new with REV\TeX4.2,
starting with the \texttt{video} environment, which is in the same category with
\texttt{figure} and \texttt{table}.%
\begin{video}
\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1a.mpg}{\includegraphics{vid_1a}}%
 \quad
\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1b.mpg}{\includegraphics{vid_1b}}
 \setfloatlink{http://link.aps.org/multimedia/PRSTPER/v4/i1/e010101}%
 \caption{\label{vid:PRSTPER.4.010101}%
  Students explain their initial idea about Newton's third law to a teaching assistant.
  Clip (a): same force.
  Clip (b): move backwards.
 }%
\end{video}
The \verb+\setfloatlink+ command causes the title of the video to be a hyperlink to the
indicated URL; it may be used with any environment that takes the \verb+\caption+
command.
The \verb+\href+ command has the same significance as it does in the context of
the \texttt{hyperref} package: the second argument is a piece of text to be
typeset in your document; the first is its hyperlink, a URL.

>>>>

\author{Kosala Herath,}
 % \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
\author{Malin Premaratne}%
\affiliation{%
 Advanced Computing and Simulation Laboratory(A$\chi$L), Department of Electrical and Computer Systems Engineering,\\
 Monash University, Clayton, Victoria 3800, Australia
}%

% \collaboration{MUSO Collaboration}%\noaffiliation
%
% \author{Charlie Author}
%  \homepage{http://www.Second.institution.edu/~Charlie.Author}
% \affiliation{
%  Second institution and/or address\\
%  This line break forced% with \\
% }%
% \affiliation{
%  Third institution, the second for Charlie Author
% }%
% \author{Delta Author}
% \affiliation{%
%  Authors' institution and/or address\\
%  This line break forced with \textbackslash\textbackslash
% }%
%
% \collaboration{CLEO Collaboration}%\noaffiliation

@@

\begin{abstract}
[**ABSTRACT] An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article.
\begin{description}
\item[Usage]
Secondary publications and information retrieval purposes.
\item[Structure]
You may use the \texttt{description} environment to structure your abstract;
use the optional argument of the \verb+\item+ command to give the category of each item.
\end{description}
\end{abstract}

@@

\section{\label{sec:introduction} INTRODUCTION}

@@

The \verb+\label{#1}+ should appear
within the section heading,
within the footnote text,
within the equation, or
within the table or figure caption.
The \verb+\ref{#1}+ command
is used in text at the point where the reference is to be displayed.
Some examples: Section~\ref{sec:level1} on page~\pageref{sec:level1},
Table~\ref{tab:table1},%
\begin{table}[b]%The best place to locate the table environment is directly after its first reference in text
\caption{\label{tab:table1}%
A table that fits into a single column of a two-column layout.
Note that REV\TeX~4 adjusts the intercolumn spacing so that the table fills the
entire width of the column. Table captions are numbered
automatically.
This table illustrates left-, center-, decimal- and right-aligned columns,
along with the use of the \texttt{ruledtabular} environment which sets the
Scotch (double) rules above and below the alignment, per APS style.
}
\begin{ruledtabular}
\begin{tabular}{lcdr}
\textrm{Left\footnote{Note a.}}&
\textrm{Centered\footnote{Note b.}}&
\multicolumn{1}{c}{\textrm{Decimal}}&
\textrm{Right}\\
\colrule
1 & 2 & 3.001 & 4\\
10 & 20 & 30 & 40\\
100 & 200 & 300.0 & 400\\
\end{tabular}
\end{ruledtabular}
\end{table}
and Fig.~\ref{fig:epsart}.%
\begin{figure}[b]
\includegraphics{figures/fig_1}% Here is how to import EPS art
\caption{\label{fig:epsart} A figure caption. The figure captions are
automatically numbered.}
\end{figure}

@@

Use the \texttt{figure} environment for a figure, the \texttt{table} environment for a table.
In each case, use the \verb+\caption+ command within to give the text of the
figure or table caption along with the \verb+\label+ command to provide
a key for referring to this figure or table.
The typical content of a figure is an image of some kind;
that of a table is an alignment.%
\begin{figure*}
\includegraphics{figures/fig_2}% Here is how to import EPS art
\caption{\label{fig:wide}Use the figure* environment to get a wide
figure that spans the page in \texttt{twocolumn} formatting.}
\end{figure*}
\begin{table*}
\caption{\label{tab:table3}This is a wide table that spans the full page
width in a two-column layout. It is formatted using the
\texttt{table*} environment. It also demonstates the use of
\textbackslash\texttt{multicolumn} in rows with entries that span
more than one column.}
\begin{ruledtabular}
\begin{tabular}{ccccc}
 &\multicolumn{2}{c}{$D_{4h}^1$}&\multicolumn{2}{c}{$D_{4h}^5$}\\
 Ion&1st alternative&2nd alternative&lst alternative
&2nd alternative\\ \hline
 K&$(2e)+(2f)$&$(4i)$ &$(2c)+(2d)$&$(4f)$ \\
 Mn&$(2g)$\footnote{The $z$ parameter of these positions is $z\sim\frac{1}{4}$.}
 &$(a)+(b)+(c)+(d)$&$(4e)$&$(2a)+(2b)$\\
 Cl&$(a)+(b)+(c)+(d)$&$(2g)$\footnotemark[1]
 &$(4e)^{\text{a}}$\\
 He&$(8r)^{\text{a}}$&$(4j)^{\text{a}}$&$(4g)^{\text{a}}$\\
 Ag& &$(4k)^{\text{a}}$& &$(4h)^{\text{a}}$\\
\end{tabular}
\end{ruledtabular}
\end{table*}

@@

Video~\ref{vid:PRSTPER.4.010101}
illustrates several features new with REV\TeX4.2,
starting with the \texttt{video} environment, which is in the same category with
\texttt{figure} and \texttt{table}.%
\begin{video}
\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1a.mpg}{\includegraphics{videos/vid_1a}}%
 \quad
\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1b.mpg}{\includegraphics{videos/vid_1b}}
 \setfloatlink{http://link.aps.org/multimedia/PRSTPER/v4/i1/e010101}%
 \caption{\label{vid:PRSTPER.4.010101}%
  Students explain their initial idea about Newton's third law to a teaching assistant.
  Clip (a): same force.
  Clip (b): move backwards.
 }%
\end{video}
The \verb+\setfloatlink+ command causes the title of the video to be a hyperlink to the
indicated URL; it may be used with any environment that takes the \verb+\caption+
command.
The \verb+\href+ command has the same significance as it does in the context of
the \texttt{hyperref} package: the second argument is a piece of text to be
typeset in your document; the first is its hyperlink, a URL.

### 2021-06-27 paper/v1.0/sections/1_introduction.tex
Add paper sections

\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{graphicx}
\usepackage{url}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\usepackage{mathtools}

\numberwithin{equation}{subsection}
\newcommand{\mb}[1]{\mathbf{#1}}
\title{Floquet-Drude Conductivity in Dressed Quantum Hall Systems}
\author{Kosala Sananthana Herath}
\numberwithin{equation}{section}

\begin{document}

\maketitle

\section*{Abstract}

@@

\section*{Purpose of the Study}

@@

In this study we develop a genralized mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [1,2]. In addition, we demonstrate that our generalized model is agreed with the state of art conductivity model [5] for specalized quantum Hall system which has been considered without the external dressing field.

\section*{Research Method}

In this analysis we consider 2DEG which has been distrubuted in confined $(x,y)$ plane in configuration space.
\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.9]{figures/fig0.pdf}
  \caption{Confined 2DEG in configuration space with the size of $A=L_xL_y$.}
  \label{fig:1}
\end{figure}

We examined the properties of 2DEG with stationary magnetic field which directed on $z$ axis and a linearly $y$-polarized strong electomagnetic wave (dressing field) with electric field which also propagate in $z$ direction.
\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.9]{figures/fig1.pdf}
  \caption{Stationary magnetic filed (blue color) and Strong EM wave (red color) applied to the 2DEG.}
  \label{fig:2}
\end{figure}

In the state of art conductivity model [5] which only describes trasport properies quantum Hall system without external dressing field has used an approximation equivalent to asssumin that the broadening of a Landau level due to disorder is represented by a constant broadening. However, from the Floquet-Drude conductivity model we have foud that we can manipulate the impurity broadening using intense high-frequency electromagnetic waves and this study we have developed a mathematical formula to calculate this Landau energy level broadening and using those values we were able to evaluate diagonal elements of conductivity tensor in dressed quantum Hall systems. Ultimately we can express the normalized conductivity for a quantum Hall system with linearly polarized drerssing field analytically as follows
\begin{equation*}
    \sigma^{dd}(X_F,\tilde{I}) =
    \sum_{n}
    \frac{\qty(n+1)}{\gamma_{n}\gamma_{n+1}}
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{\gamma_{n+1}})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{\gamma_{n}})^2
      }
    ]
\end{equation*}
where $X_F$ is normalized Fermi level and $\gamma_n$ represnts normalized energy band broadening of $n$-th Landau level. This $\gamma_n$ only depends on the normalized intensity value of dressing field $\tilde{I}$. We can choose the direction $d$ of the diagonal conductivity tensor element from $(x,y)$.

\section*{Outcomes and Discussion}

First we have identified that we can control the Landau level broadening using the dressing field intensity as given in the Figure \ref{fig:3}.
\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.6]{figures/fig3.pdf}
  \caption{The dependence of the normalized Landau level broadening on the dressing field intensity for different Landau levels ($N=0,1,2,3,4$).}
  \label{fig:3}
\end{figure}

As mentioned in above derived analytical expression the changes can be done to the transverse conductivity using external dressing field. As given in Figure \ref{fig:4} and \ref{fig:5} we can manipulate the conductivity using external dressing field.

\begin{figure}[ht!]
  \centering
  \includegraphics[scale=1]{figures/fig4.pdf}
  \caption{Normalized transverse conductivity against Fermi level ($X_F$) with different intensities ($\tilde{I}$) of dressing field.}
  \label{fig:4}
\end{figure}

When the dressing field's intensity increase the broadening of energy bands of Landau levels get reduced and the conductivity also get decrease in all the regions except the peak points of each level. Using this manipulation we can filter the conductivity which is change with the Fermi level. Since Fermi level can be change with the applied gate voltage of the material this can be used as a 2D switch for optoelectonic applications. However with the existance of  external dressing field we can fine tune the switching mechanism and it is an exceptional advantage in optoelectonic applications.

\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.9]{figures/fig5.pdf}
  \caption{$3$rd Landau level's normalized transverse conductivity against Fermi level ($X_F$) with different intensities ($\tilde{I}$) of dressing field.}
  \label{fig:5}
\end{figure}

Now we can compare our result with previous studies to the check the validity of the outcomes. In the research done by K. Dini et al. [6] has demonstrated that the diagonal elements of conductivity tensor in a quantum Hall system can manipute with apllying high intense light as given in Figure \ref{fig:6}. However the behaviour of the conductivity with the Fermi level is not accurate as given in the state of art study [5] which has been represent in Figure \ref{fig:7}. When we consider the our outcome which derived using novel Floquet-Drude conductivity model, we can see that it agree with the results given in the much accurate study [5]. However, our study present a more generalized mathematical model rather than the specific scenario studied in the study [6].

\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.3]{figures/fig6.pdf}
  \caption{The dependence of the longitudinal conductivity $\sigma_{xx}$ , on
the Fermi energy $\varepsilon_F$. The solid line describes the conductivity
of unirradiated 2DEG, whereas the dotted line corresponds to the
conductivity at the irradiation intensity $I = 600 \; \text{W/cm2}$. The inset
shows the difference between these two conductivities. (from K.Dini at el. [6])}
  \label{fig:6}
\end{figure}

\newpage
\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.3]{figures/fig7.pdf}
  \caption{The diagonal and the off-diagonal components
of the conductivity tensor modified to account for the long-range potential. The
horizontal axis is the inverse magnetic field. (from A. Endo at el. [5])}
  \label{fig:7}
\end{figure}

We can conclude that the using external dressing field we can manipulate the magneto-electric properties of a quantum Hall system and in this study we were able to demonstrate that using Floquet-Drude conductivity method we can derive a more accurate generalized mathematical model that describe the trasport properties of quantum Hall syatems. Therefore this theory describes that the  dressing field can be used as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-optoelectonic devices.

\section*{Reference}

[1] M. Wackerl, P. Wenk, and J. Schliemann, Floquet-Drude Conductivity, Phys. Rev. B 101, 184204 (2020).

\noindent
[2] M. Wackerl, Transport in Periodically Driven Systems, University of Regensburg, (2020).

\noindent
[3] T. Ando and Y. Uemura, Theory of Quantum Transport in a Two-Dimensional Electron System under Magnetic Fields. I. Characteristics of Level Broadening and Transport under Strong Fields, J. Phys. Soc. Jpn. 36, 959 (1974).

\noindent
[4] T. Ando, A. B. Fowler, and F. Stern, Electronic Properties of Two-Dimensional Systems, Rev. Mod. Phys. 54, 437 (1982).

\noindent
[5] A. Endo, N. Hatano, H. Nakamura, and R. Shirasaki, Fundamental Relation between Longitudinal and Transverse Conductivities in the Quantum Hall System, J. Phys.: Condens. Matter 21, 345803 (2009).

\noindent
[6] K. Dini, O. V. Kibis, and I. A. Shelykh, Magnetic Properties of a Two-Dimensional Electron Gas Strongly Coupled to Light, Phys. Rev. B 93, 235411 (2016).

\end{document}

>>>>

@@

@@

In this study we develop a genralized mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [1,2]. In addition, we demonstrate that our generalized model is agreed with the state of art conductivity model [5] for specalized quantum Hall system which has been considered without the external dressing field.  Therefore this theory describes that the dressing field can be used as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-optoelectonic devices.
